\documentclass{amsart}

\begin{document}
\begin{ttfamily}
    \begin{tabbing}
        Print\=Time\\
        \>Block\=[timing],\\
        \>\>timing = Timing[expr];\\
        (careful with initialization)\kill
        \>\>Print[ timing[[1]] ];\\
        \>]\\
        End[]
    \end{tabbing}
\end{ttfamily}

\begin{ttfamily}
    \begin{tabbing}
        \hspace*{.25in}\=\hspace{2ex}\=\hspace{2ex}\=\hspace{2ex}\kill
        \> $k := 1$\\
        \> $l_k := 0$; $r_k := 1$\\
        \> loop\\
        \>\> $m_k := (l_k + r_k)/2$\\
        \>\> if $w < m_k$ then\\
        \>\>\> $b_k := 0$; $r_k := m_k$\\
        \>\> else if $w >m_k$ then\\
        \>\>\> $b_k := 1$; $l_k := m_k$\\
        \>\> end if\\
        \>\> $k := k+1$\\
        \> end loop
    \end{tabbing}
\end{ttfamily}

\begin{ttfamily}
    \begin{tabbing}
        This is short.\=\\
        This is much longer,\> and jumps back.
    \end{tabbing}
\end{ttfamily}

\clearpage

It's not that I'm afraid to die. I just don't
want to be there when it happens.
\emph{Woody Allen}

Literature is news that STAYS news.
\emph{Ezra Pound}

\begin{quote}
    It's not that I'm afraid to die. I just don't
    want to be there when it happens.
    \emph{Woody Allen}

    Literature is news that STAYS news.
    \emph{Ezra Pound}
\end{quote}

\begin{quotation}
    KATH: Can he be present at the birth of his child?

    ED: It's all any reasonable child can expect
    if the dad is present at the conception.
    \begin{flushright}\emph{Joe Orton}\end{flushright}
\end{quotation}

\begin{verse}
    I think that I shall never see\\
    A poem lovely as a tree.

    Poems are made by fools like me,\\
    But only God can make a tree.
    \begin{flushright}
        \emph{Joyce Kilmer}
    \end{flushright}
\end{verse}

Formula (2) in Section 3 should be typed as follows:
\begin{verbatim}
\begin{equation}
    D = \{ x_0 \mid x_0 \Rightarrow a_1 \} \tag{2}
\end{equation}
\end{verbatim}
please make the necessary corrections.

Some European e-mail addresses contain \%;
recall that you have to type \verb+\%+ to get \%.
\verb*!$\sin(\pi/2 + \alpha)$!
\end{document}
